Wheels of Misfortune: Exploring Auto Theft Trends in Ottawa

### 2024-04-22 paper/paper.qmd
more graphs

theft_recovery |>
  ggplot(mapping = aes(x = theft_year, fill = recovered)) +
  geom_bar(position = "dodge2") +
  labs(x = "Age group", y = "Number of observations", fill = "Vote") +
  theme(legend.position = "bottom")
```
```{r}
#| label: theft-neighborhoods
#| fig-cap: "Recovery Rates from 2018 - 2023"
#| echo: false
#| warning: false
#| message: false

@@

theft_recovery |>
  ggplot(aes(x = neighbourhood, y = n, fill = n)) +  # Use n as the fill aesthetic
  geom_bar(stat = "identity") +
  theme_minimal() + theme(legend.position = "bottom") + 
  labs(x = "Vehicle Brand", y = "Count", fill = "Count", title = "Top 10 Brands with Most Auto Thefts in 2022") 
```

>>>>

theft_recovery |>
  ggplot(mapping = aes(x = theft_year, fill = recovered)) +
  geom_bar(position = "dodge2") +
  labs(x = "Age group", y = "Number of observations", fill = "Vote") +
  theme(legend.position = "bottom")

# Merging 'theft_recovery' dataframe with 'auto_Data'
merged_data <- merge(auto_Data, theft_recovery, by = "theft_year", all.x = TRUE)

# Plotting the merged data as a line graph
ggplot(merged_data, aes(x = theft_year, y = recovered)) +
  geom_line() + 
  geom_point() +
  labs(x = "Year", y = "Count") +
  theme_minimal()
```
```{r}
#| label: theft-neighborhoods
#| fig-cap: "Recovery Rates from 2018 - 2023"
#| echo: false
#| warning: false
#| message: false

@@

years_vehicle <- auto_Data |>
  select(vehicle_year) |> 
  count(vehicle_year)

theft_recovery |>
  ggplot(aes(x = neighbourhood, y = n, fill = n)) +  # Use n as the fill aesthetic
  geom_bar(stat = "identity") +
  theme_minimal() + theme(legend.position = "bottom") + 
  labs(x = "Vehicle Brand", y = "Count", fill = "Count", title = "Top 10 Brands with Most Auto Thefts in 2022")

library(ggplot2)

# Assuming 'years_vehicle' is your data frame

years_vehicle <- years_vehicle |>
  mutate(vehicle_year = as.numeric(vehicle_year))  # Convert to numeric if 'vehicle_year' is factor

# Create a scatter plot
ggplot(years_vehicle, aes(x = vehicle_year, y = n, fill = n)) +
  geom_point() +  # Use geom_point() for scatter plot
  scale_x_continuous(limits = c(1930, 2024)) +  # Adjust the x-axis limits here
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  labs(x = "Vehicle Brand", y = "Count", fill = "Count", title = "Top 10 Brands with Most Auto Thefts in 2022")

```{r}
#| label: theft-neighborhoods
#| fig-cap: "Recovery Rates from 2018 - 2023"
#| echo: false
#| warning: false
#| message: false

theft_recovery <- auto_Data |>
  select(neighbourhood) |> 
  count(neighbourhood)

library(ggplot2)

# Assuming 'years_vehicle' is your data frame

years_vehicle <- theft_recovery |>
  mutate(vehicle_year = as.numeric(neighbourhood))  # Convert to numeric if 'vehicle_year' is factor

# Create a scatter plot
ggplot(years_vehicle, aes(x = neighbourhood, y = n, fill = neighbourhood)) +
  geom_point() +  
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  labs(x = "Vehicle Brand", y = "Count", fill = "Count", title = "Top 10 Brands with Most Auto Thefts in 2022")
